Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-26 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
%\vspace{-1.3cm}
    \centering
    \includegraphics[width=\columnwidth]{figures/CHEMPY_TNG_yields.png}
    \vspace{-.25cm}
    \caption{Joint posterior for global galactic parameters $\alpha_{\rm IMF}$ and $\log_{10}(\rm N_{Ia})$ of $1,000$ stars. The ground truth value is shown by the black dot, the posterior mean of the SBI inference is shown with the red star and white and black ellipses show the $1-3\sigma$ contours of our inference. See Sec.~\ref{subsec:chempy_tng} for a full description.}
    \label{fig:CHEMPY_TNG_sbi} 
    \script{chempy_tng_inference.py}
\end{figure}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/CHEMPY_alternative_yields_Nstar_comp.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for the mock data created with a different yield set than the training data. See Sec.~\ref{subsec:mocks_wrong_yield} for a full description.}
    \label{fig:CHEMPY_alt_N_star_analysis}
    \script{chempy_alt_yield_inference.py}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/TNG_sim_Nstar_comp.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for the mock data taken from an IllustrisTNG Milky Way-like galaxy. See Sec.~\ref{subsec:tng_sim} for a full description.}
    \label{fig:TNG_N_star_analysis}
    \script{tng_inference.py}
\end{figure*}

>>>>

\begin{figure}
%\vspace{-1.3cm}
    \centering
    \includegraphics[width=\columnwidth]{figures/CHEMPY_TNG_yields.png}
    \vspace{-.25cm}
    \caption{Joint posterior for global galactic parameters $\alpha_{\rm IMF}$ and $\log_{10}(\rm N_{Ia})$ of $100$ stars. The ground truth value is shown by the red star, the posterior mean of the SBI inference is shown with the black dot and white ellipses show the $1-3\sigma$ contours of our inference. The gray ellipses show the results for HMC inference performed by \citet{Philcox_2019}. See Sec.~\ref{subsec:chempy_tng} for a full description.}
    \label{fig:CHEMPY_TNG_sbi} 
    \script{chempy_tng_inference.py}
\end{figure}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/CHEMPY_alternative_yields_Nstar_comp.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for the mock data created with a different yield set than the training data. See Sec.~\ref{subsec:mocks_wrong_yield} for a full description.}
    \label{fig:CHEMPY_alt_N_star_analysis}
    \script{chempy_alt_yield_inference.py}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/TNG_sim_Nstar_comp.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for the mock data taken from an IllustrisTNG Milky Way-like galaxy. See Sec.~\ref{subsec:tng_sim} for a full description.}
    \label{fig:TNG_N_star_analysis}
    \script{tng_inference.py}
\end{figure*}
